Hybrid platforms and bargaining

### 2023-04-19 src/presentation/topics_talk.qmd
Add model section to the topics talk

>>>>

# Model

## Players

::: {.fragment}
 - One platform: $P$
   - Without the platform, no value can be created
   - Might have its own products (hybrid mdoe)
:::
::: {.fragment}
 - A continuum of potential fringe entrants: $F_i, i \in \mathbb{R}_0^+$
   - Infinitesimal size
   - Have one product each
   - Can only sell through the platform
:::

## Production

Reduced-form approach: assume some function for total profit:

::: {.fragment}
$$
f(N_P, N_F)
$$
:::

::: {.fragment}
 - $N_P$ is the number of platform products
 - $N_F$ is the number of fringe products/firms
 - Assume that $f$ is increasing in both arguments
:::

## Profit sharing

 - Platform gets $$ \pi_P(N_P, N_F) = \int_0^1 w(s) f(N_P, sN_F) \mathrm{d}s $$
 - Fringe gets the rest

::: {.fragment}
 - Based on the Shapley-value 
   - Bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
   - Precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
 - $w(s)$ is a weighting function with $\int_0^1 w(s) \mathrm{d}s = 1$
   - Related to the weighted value for a certain class of functions
:::

## Some simple comparative statics

::::: {.columns}

:::: {.column width="40%"}

::: {.fragment fragment-index=1}
 - The platform likes being hybrid
$$
\small
\frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0
$$
:::
::: {.fragment fragment-index=2}
 - It depends™ for the fringe
$$
\begin{align*}
\small\mathrm{sign} \left( \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} \right) = \\
\small\mathrm{sign} \left( \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} \right)
\end{align*}
$$
:::

::::

:::: {.column width="60%"}

::: {.r-stack}

::: {.fragment fragment-index=1}

:::
::: {.fragment fragment-index=2}

::::

:::::

## Entry and equilibrium

Now let us endogeneize the number of fringe entrants!

::: {.fragment}
 - Unlimited number of potential entrants
:::
::: {.incremental}
 - Timing
    - Hybrid mode is exogeneously determined $\to N_P$
    - Each fringe firm decides whether to invest at cost $I_F$ $\to N_F$
    - Platform and firms produce and sell products $\to f(N_P, N_F)$
    - Profits are shared according to previous rule $\to \pi_P(N_P, N_F), \pi_F(N_P, N_F)$
:::

## Equilibrium

::: {.incremental}
 - Free entry equilibrium: fringe firms make zero net profits
   $$ \pi_F(N_P, N_F^*) = I_F N_F^* $$
 - In order to guarantee uniqueness, let us assume
   $$
   \scriptsize
   \begin{gather*}
       f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \mathrm{d}s \\
       \text{or} \\
       f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \mathrm{d}s.
   \end{gather*}
   $$
     - Holds for certain interesting cases, such as the example application
:::

## Equilibrium comparative statics

::::: {.columns}

:::: {.column width="40%"}

::: {.fragment fragment-index=1}
 - Hybrid mode reduces fringe entry
$$
\small
\frac{\partial N_F^*}{\partial N_P} < 0
$$
:::
::: {.fragment fragment-index=2}
 - And, under certain conditions, total profits
$$
\small\text{Let } f(N_P, N_F) = g(\alpha N_P + \beta N_F)
$$
$$
\small\text{Then } \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
$$
:::

::::

:::: {.column width="60%"}

::: {.r-stack}

::: {.fragment fragment-index=1}

:::
::: {.fragment fragment-index=2}

::::

:::::

# More concrete example

# Summary
